Supplementary Figures

### 2019-05-13 bmc_article.tex
...

Doublets, defined as two cells sequenced under the same cellular barcode (for instance as a result of being captured in the same droplet), are fairly frequent in scRNAseq datasets, with estimates ranging from X to Y \% [REFs]. While doublets of the same cell type are relatively innocuous for most downstream applications due to their conservation of the relative expression between genes, doublets formed from different cell types or states are likely to be misclassified and could potentially distort downstream analysis. In some cases, doublets can be identify through their unusually high number of reads and detected features, but this is not always the case (Supplementary Figure 2). A number of methods were developed to identify doublets, in most cases by comparing each cell to artificially-created doublets [REFs]. We therefore first evaluated the capacity of these methods to detect doublets using the two 10x datasets produced by Tian et al. (\citey{mixology}) with cells of different genetic identity, and for which therefore SNP information can be used as ground truth. We tested DoubletFinder [REF] and scran's doubletCells [REF], both of which use similarity to artificial doublets, and scds [REF], which relies on a combination of coexpression and binary classification. DoubletFinder integrates a thresholding based on the proportion of expected doublets, while scran and scds return scores which must be manually thresholded. In these cases, we ensured that the right number of cells would be called doublets.

In addition to these methods, we reasoned that an approach such as DoubletFinder could be considerably sped up by being applied directly on counts and by using a pre-clustering to create neotypic doublets more efficiently. We therefore developed a simple and fast package implementing this for doublet detection, with the added perk of accounting for uncertainty in the expected doublet rate and using meta-cells from the clusters to even include triplets.

While most methods accurately identified the doublets in the 3 cell lines dataset (mixology10x3cl), the 5 lines dataset (mixology10x5cl) proved more difficult [Figure]. Of note, our method ran in a fraction of the time required by other methods, and nevertheless proved more accurate [Figure]. We therefore tested whether this method also improved the accuracy of the clustering across all benchmark datasets, and found that it did [Figure].

@@

Beyond doublets, a dataset might include low-quality cells whose elimination would reduce noise. This has for instance been demonstrated for cells that have a high content of mitochondrial reads, often as a result of cell degradation [REF]. A common practice is to exclude cells that differ considerably from most other cells on the basis of some such properties, for instance through the `isOutlier` function of `scater` which measures, for a given control property, the number of median absolute deviation of each cell from the mean of all cells. Supplementary Figure 1 shows some of the typical cell properties commonly used. Of note, these properties tend to be correlated, but are not always: for instance, while a high proportion of mitochondrial reads is often correlated with a high proportion of the counts in the top features, there can also be other reasons for an over-representation of highly-expressed features [Supplementary figure?]. In addition, in our experience 10x datasets also exhibit a very tight correlation between the total counts and the total features even across very different cell types (Supplementary Figure 4). We therefore also measure the ratio between the two, and treat cells strongly departing from this trend with suspicion.

Reasoning that the cells we wish to eliminate are cells that would be misclassified, we measured the rate of misclassification of each cell in each dataset across a variety of clustering pipelines, correcting for the median misclassification rate of the subpopulation. We then evaluated what properties could be predictive of misclassification [Supplementary]. The only feature that consistently stood out across multiple datasets was that cells with a very high read counts have a higher chance of being misclassified.

@@

A first observation was that very stringent filtering (removing up to 20\% of the cells) was not generally associated with an increase in accuracy of the clustering [Supplementary], and it somewhat expectedly tended to be biased towards the exclusion of specific subpopulations. We next investigated the criteria [Supplementary]. Interestingly, while filtering out cells with very high total counts and high total features has a significant positive impact on ARI, filtering the lower end of the distribution did not appear to do so, most likely because of prior droplet selection steps.

Surprisingly, filtering out on the basis of the proportion of mitochondrial counts or of counts in the top features did not significantly improve the clustering; however, when testing for the impact of the proportion of mitochondrial counts in the absence of other covariates (i.e. total counts and features), it did have a significant positive impact, suggesting that ‘bad’ cells are anyway excluded on the basis of other distributions. This being said, it must be noted that none of the benchmark datasets has a very high mitochondrial content, and that this filtering might well be important in other datasets. However, filtering solely based on deviations from the distribution might be inadequate when the distribution is tight; in our experience, the proportion of mitochondrial counts in otherwise ‘healthy’ cells can vary up to 8-12\% depending on the tissue. We therefore recommend using a combination of fixed and deviation based threshold, e.g. x $>$ 0.08 and x $>$ 2.5*MADs.

When focusing on the 10x datasets, anova suggests that increasing the number of distribution on which a cell should be an outlier in order to be excluded (`filt.times`) had a significant positive impact on ARI while greatly reducing the of excluded cells; in contrast, increasing the number of MADs leads to a (less robust) decrease in ARI. This suggests that having stringent thresholds but requiring to be an outlier on multiple distributions is preferable.

>>>>

Doublets, defined as two cells sequenced under the same cellular barcode (for instance as a result of being captured in the same droplet), are fairly frequent in scRNAseq datasets, with estimates ranging from 1 to 10\% depending on the platform and cell concentration used \citep{bloom_estimating_2018,kang_multiplexed_2018}. While doublets of the same cell type are relatively innocuous for most downstream applications due to their conservation of the relative expression between genes, doublets formed from different cell types or states are likely to be misclassified and could potentially distort downstream analysis. In some cases, doublets can be identified through their unusually high number of reads and detected features, but this is not always the case (Supplementary Figure 2). A number of methods were developed to identify doublets, in most cases by comparing each cell to artificially-created doublets [REFs]. We therefore first evaluated the capacity of these methods to detect doublets using the two 10x datasets produced by Tian et al. (\citey{tian_mixology_2018}) with cells of different genetic identity, and for which therefore SNP information can be used as ground truth. We tested DoubletFinder [REF] and scran's doubletCells [REF], both of which use similarity to artificial doublets, and scds [REF], which relies on a combination of coexpression and binary classification. DoubletFinder integrates a thresholding based on the proportion of expected doublets, while scran and scds return scores which must be manually thresholded. In these cases, we ensured that the right number of cells would be called doublets.

In addition to these methods, we reasoned that an approach such as DoubletFinder could be considerably sped up by being applied directly on counts and by using a pre-clustering to create neotypic doublets more efficiently. We therefore developed a simple and fast package implementing this for doublet detection, with the added perk of accounting for uncertainty in the expected doublet rate and using meta-cells from the clusters to even include triplets (see methods).

While most methods accurately identified the doublets in the 3 cell lines dataset (mixology10x3cl), the 5 lines dataset (mixology10x5cl) proved more difficult (Figure 1B). Our method achieved the best accuracy while running in a very reasonable time (Figure 1). Across datasets, cells called as doublets tended to be classified in the wrong cluster more often than other cells (Figure 1D). We therefore tested whether this method also improved the accuracy of the clustering across all benchmark datasets, and found that it consistently did (Figure 2).

@@

Beyond doublets, a dataset might include low-quality cells whose elimination would reduce noise. This has for instance been demonstrated for cells that have a high content of mitochondrial reads, often as a result of cell degradation [REF]. A common practice is to exclude cells that differ considerably from most other cells on the basis of some such properties, for instance through the `isOutlier` function of `scater` which measures, for a given control property, the number of median absolute deviation of each cell from the mean of all cells. Supplementary Figure 1 shows the distributions of some of the typical cell properties commonly used. Of note, these properties tend to be correlated, but are not always: for instance, while a high proportion of mitochondrial reads is often correlated with a high proportion of the counts in the top features, there can also be other reasons for an over-representation of highly-expressed features (Supplementary Figure 3). In addition, in our experience 10X datasets also exhibit a very tight correlation between the total counts and the total features even across very different cell types (Supplementary Figure 4). We therefore also measure the ratio between the two, and treat cells strongly departing from this trend with suspicion.

Reasoning that the cells we wish to eliminate are cells that would be misclassified, we measured the rate of misclassification of each cell in each dataset across a variety of clustering pipelines, correcting for the median misclassification rate of the subpopulation, and then evaluated what properties could be predictive of misclassification (Supplementary Figures 5-7). We could not identify any property or simple combination thereof which would be consistently predictive of misclassification; the only feature that consistently stood out across multiple datasets (the Zheng datasets) was that cells with a very high read counts have a higher chance of being misclassified.

@@

A first observation was that very stringent filtering (removing up to 20\% of the cells) was not generally associated with an increase in accuracy of the clustering (Supplementary Figure 8A). Moreover, stringent filtering tended to be biased towards the exclusion of specific subpopulations (Supplementary Figure 8B). Indeed, applying the same filtering criteria on individual clusters of cells (identified through scran's `quickCluster` method) resulted in nearly no cell being filtered out, which suggests that filtering on the global population tends to discard cells of subpopulations with more extreme properties, rather than `bad` cells.

We next investigated the contribution of various criteria individually (Supplementary Figure 9). Interestingly, regression analysis suggests that increasing the number of distributions on which a cell must deviate in order to be excluded tended to be positively associated with ARI, while increasing the number of median absolute deviations required to be an outlier as associated with a decrease in ARI. We therefore suggest excluding cells that are outliers on more than 1 distributions. The impact of filtering on the basis of total counts or feature counts was not always robust, nor always positive, and we could detect no significant impact of filtering on the basis of the proportion of mitochondrial reads - however it must be said that the benchmark datasets count very few cells with a very high proportion of mitochondrial reads (Supplementary Figure 1). We therefore suggest to keep this criterion, but in a relatively lenient fashion, and not solely based on the median absolute deviation of the distribution. Filtering solely based on deviations from the distribution might be inadequate when the distribution is tight; in our experience, the proportion of mitochondrial counts in otherwise `healthy` cells can vary up to 8-12\% depending on the tissue. We therefore recommend using a combination of fixed and deviation based threshold, e.g. x $>$ 0.08 and x $>$ 2.5*MADs.

On the basis of these observations, we defined three sets of criteria as lenient, default and stringent filtering (see methods), and investigated them further.

### 2019-05-13 main_figures/figure1_doublets.Rmd
...

```{r}
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(ROCit)
  library(cowplot)
})
# we load the dataset
sce <- readRDS("../datasets/mixology10x5cl.SCE.rds")
CD <- as.data.frame(colData(sce))
```

```{r}
truth <- factor(CD$demuxlet_cls, c("SNG","DBL"))
roclist <- lapply( list(plDoubletFinder=CD$pldf.ratio,
                        DoubletFinder.p=CD$doubletFinder.pANN_0.25_0.02_82,
                        scran.score=CD$scran.doubletscore,
                        scds.hybrid=CD$hybrid_score), 
                   class=truth, FUN=rocit)
colors <- c("blue","red","black","pink")
plot(roclist[[1]], lwd=2, col=c(colors[[1]], "grey"), legend=FALSE, YIndex=FALSE, main="mixology10x5cl")
for(i in 2:length(roclist)){
  lines(roclist[[i]]$FPR, roclist[[i]]$TPR, lwd=2, col=colors[[i]])
}
legend("bottomright", fill=colors, legend=names(roclist))
```

>>>>

```{r}
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(ROCit)
  library(ggplot2)
  library(cowplot)
})
theme_set(theme_cowplot(font_size = 12))

# we load the dataset
lf <- list.files("../datasets/", pattern="SCE", full.names=TRUE)
names(lf) <- sapply(strsplit(basename(lf),".",fixed=TRUE), head, 1)
CDs <- lapply(lf, FUN=function(x){ as.data.frame(colData(readRDS(x))) })
```

```{r}
colors <- c("#4477AA", "#117733", "#DDCC77", "#CC6677")
CD <- CDs$mixology10x3cl
truth <- factor(CD$demuxlet_cls, c("SNG","DBL"))
roclist <- lapply( list(scDblFinder=CD$pldf.ratio,
                        scds.hybrid=CD$hybrid_score,
                        scran.score=CD$scran.DblScore),
                   class=truth, FUN=rocit)
d <- data.frame( method=rep( c("scDblFinder","scds","scran"),
                             sapply(roclist, FUN=function(x) length(x$TPR)) ),
                 FPR=unlist(lapply(roclist,FUN=function(x) x$FPR)),
                 TPR=unlist(lapply(roclist,FUN=function(x) x$TPR)) )
p1 <- ggplot(d, aes(FPR, TPR, colour=method)) + geom_line(size=1.5) + ggtitle("mixology10x3cl")
p1 <- p1 + theme(legend.position = c(0.6, 0.3)) + scale_color_manual(values=colors[-2])

CD <- CDs$mixology10x5cl
truth <- factor(CD$demuxlet_cls, c("SNG","DBL"))
roclist <- lapply( list(scDblFinder=CD$pldf.ratio,
                        DoubletFinder=CD$doubletFinder.pANN_0.25_0.02_82,
                        scds=CD$hybrid_score,
                        scran=CD$scran.DblScore), 
                   class=truth, FUN=rocit)
d <- data.frame( method=factor( rep(names(roclist), sapply(roclist, FUN=function(x) length(x$TPR))), levels=names(roclist)),
                 FPR=unlist(lapply(roclist,FUN=function(x) x$FPR)),
                 TPR=unlist(lapply(roclist,FUN=function(x) x$TPR)) )
p2 <- ggplot(d, aes(FPR, TPR, colour=method)) + geom_line(size=1.5) + ggtitle("mixology10x5cl")
p2 <- p2 + theme(legend.position = c(0.6, 0.3)) + scale_color_manual(values=colors)
```

```{r}
rt <- data.frame( time=c(12.83, 41.46, 25.08, NA, 56.15, 310.24, 268.93, 722.031),
                  method=rep(c("scds", "scran", "scDblFinder", "DoubletFinder"),2),
                  dataset=rep(c("mixology10x3cl", "mixology10x5cl"), each=4))
p3 <- ggplot(rt, aes(method, time, fill=method)) + geom_col() + scale_color_manual(values=colors) + facet_wrap(~dataset, scale="free", nrow=2) + coord_flip() + ylab("Wall-time, in seconds") + theme(legend.position="none", axis.title.y=element_blank(), plot.margin=unit(c(1,2,1,1),"lines"))
```

```{r}
mis <- readRDS("../data/misclassification.rds")
dbl <- lapply(CDs, FUN=function(x) x[,c("pldf.ratio","pldf.class")])
dbl <- dbl[intersect(names(dbl),names(mis))]
for(n in names(dbl)){
  dbl[[n]]$pct_misclassified_cor <- mis[[n]]$corrected_pct_mis[row.names(dbl[[n]])]
  dbl[[n]]$pct_misclassified <- mis[[n]]$pct_misclassified[row.names(dbl[[n]])]
}
d <- as.data.frame(data.table::rbindlist(dbl, idcol="dataset"))
p4 <- ggplot(d, aes(pldf.class, pct_misclassified_cor, fill=pldf.class)) + geom_violin() + facet_wrap(~dataset) + ggtitle("Cluster mis-assignment") + theme(axis.title.x=element_blank(), legend.position="none") + ylab("Corrected % misclassification") + stat_summary(fun.y="mean", geom="point")
```

```{r, fig.height=6, fig.width=7}
plot_grid( plot_grid(p1, p2, nrow=1, labels=LETTERS[1:2]), plot_grid(p3, p4, nrow=1, labels=LETTERS[3:4], rel_widths=c(2,3)), nrow=2)
```

**A-B** Receiver operating characteristic (ROC) curves of the tested doublet detection methods for the mixology10x3l (**A**) and mixology10x5cl (**B**) datasets. DoubletFinder failed due to an error on the mixology10x3cl dataset. **C:** Running time of the different methods. **D:** Cell called as doublets by scDblFinder tend to be more often misclassified, i.e. assigned a wrong cluster. The corrected percentage of misclassification is the proportion of times a given cell is misclassified across hundreds of clustering pipelines with various parameters, minus the median misclassification rate of the cell's subpopulation.

### 2019-05-13 supplementary_figures/supp1_dataset_description.Rmd
...

```{r mixology_doublet_featcount, fig.height=4}
plotDoublets <- function(sce, title="", mads=c(2,2.5,3), vars=c("log10_total_features", "log10_total_counts")){
  cd <- as.data.frame(colData(sce))
  p <- ggplot(cd, aes_string(x=vars[1], y=vars[2], colour="demuxlet_cls")) + geom_point()
  p <- p + geom_point(data=cd[which(cd$demuxlet_cls=="DBL"),], size=3)
  lt <- c("solid","dashed","dotted","dotdash")
  for(i in 1:length(mads)){
    th <- .tmads(cd[[vars[1]]], mads[i])[2]
    p <- p + geom_vline(aes_string(xintercept=th), linetype=lt[i])
    th <- .tmads(cd[[vars[2]]], mads[i])[2]
    p <- p + geom_hline(aes_string(yintercept=th), linetype=lt[i])
  }
  p  
}
pl <- list( plotDoublets(SCEs$mixology10x3cl) + ggtitle("mixology10x3cl"),
            plotDoublets(SCEs$mixology10x5cl) + ggtitle("mixology10x5cl") )
plot_grid(plotlist=pl, labels=LETTERS[1:2])
```

### Supplementary Figure `r getFigNb()`
The total counts and total features per cell of doublets versus other cells. We used the demuxlet annotation of doublets (based on SNPs) made available through CellBench. While doublets tend to have a higher total count and especially number of detected features, these features alone are not always sufficient for their identification.

# Supplementary Figure `r getFigNb(TRUE)`
[to come]
### Supplementary Figure `r getFigNb()`
Doublets that cannot be identified by our method show lower signs of being doublets.

@@

>>>>

```{r mixology_doublet_featcount, fig.height=4}
theme_set(theme_cowplot(font_size = 13))
plotDoublets <- function(sce, title="", mads=c(2,2.5,3), vars=c("log10_total_features", "log10_total_counts")){
  cd <- as.data.frame(colData(sce))
  p <- ggplot(cd, aes_string(x=vars[1], y=vars[2], colour="demuxlet_cls")) + geom_point() + theme(legend.position="none")
  p <- p + geom_point(data=cd[which(cd$demuxlet_cls=="DBL"),], size=3)
  lt <- c("solid","dashed","dotted","dotdash")
  for(i in 1:length(mads)){
    th <- .tmads(cd[[vars[1]]], mads[i])[2]
    p <- p + geom_vline(aes_string(xintercept=th), linetype=lt[i])
    th <- .tmads(cd[[vars[2]]], mads[i])[2]
    p <- p + geom_hline(aes_string(yintercept=th), linetype=lt[i])
  }
  p  
}
pl <- list( plotDoublets(SCEs$mixology10x3cl) + ggtitle("mixology10x3cl"),
            plotDoublets(SCEs$mixology10x5cl) + ggtitle("mixology10x5cl") )
plot_grid(plotlist=pl, labels=LETTERS[1:2])
```

### Supplementary Figure `r getFigNb()`
The total counts and total features per cell of doublets (red) versus other cells. We used the demuxlet annotation of doublets (based on SNPs) made available through CellBench. The lines indicate, respectively, 2, 2.5, and 3 median absolute deviations. While doublets tend to have a higher total count and especially number of detected features, these features alone are not always sufficient for their identification.

@@

\newpage
# Supplementary Figure `r getFigNb(TRUE)`

```{r cellprops_cor, fig.width=7.5, fig.height=7}
d <- data.frame( dataset=rep(names(SCEs),sapply(SCEs,ncol)), 
                 pct_counts_Mt=unlist(lapply(SCEs,FUN=function(x) x$pct_counts_Mt)),
                 pct_top_50=unlist(lapply(SCEs,FUN=function(x) x$pct_counts_in_top_50_features)),
                 log10_features=unlist(lapply(SCEs,FUN=function(x) x$log10_total_features)))
plot_grid( ggplot(d, aes(x=pct_top_50, y=pct_counts_Mt)) + geom_point() + facet_wrap(~dataset, scale="free") + geom_density_2d(),
           ggplot(d, aes(x=log10_features, y=pct_counts_Mt)) + geom_point() + facet_wrap(~dataset, scale="free") + geom_density_2d(),
           labels=LETTERS[1:2], nrow=2 )

ggplot(d, aes(x=log10_features, y=log10_counts, colour=featcount_dist)) + geom_point() + facet_wrap(~dataset, scale="free") + scale_colour_gradient2(limits=c(-0.2,0.2))
```

```{r misclass, fig.height=4}
theme_set(theme_cowplot(font_size = 11))
mis <- readRDS("../data/misclassification.rds")
pdb <- function(x, ...){
  n <- names(mis)[x]
  plotBadCells(SCEs[[n]], mis[[n]], name=n, ...)
}
pdb(2, labels=c("A",rep("",6)))
```
\vfill
```{r, fig.height=4}
pdb(3, labels=c("B",rep("",6)))
```

### Supplementary Figure `r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the mixology10x3cl (A) and mixology10x5cl (B) datasets. The percentage of misclassification refers to the frequency with which a given cell is assigned the wrong cluster (using the Hungarian algorithm for cluster matching) across several hundred clustering runs with varying parameters. Since some subpopulations tend to be more misclassified than others, the adjusted rate of misclassification (`adj_mis`) is substracted for the subpopulation median misclassification rate.

```{r, fig.height=4}
pdb(4, labels=c("A",rep("",6)))
```
\vfill
```{r, fig.height=4}
pdb(5, labels=c("B",rep("",6)))
```

### Supplementary Figure `r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the Zheng equal (A) or unequal (B) mixtures of four cell types. See Supplementary Figure `r getFigNb()-1` for more information. The only clear pattern is that cells with a high number of reads or features tend to have a higher misclassification rate.

```{r, fig.height=4}
pdb(6)
```

### Supplementary Figure `r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the Zheng mixture of 8 cell types. See Supplementary Figure `r getFigNb()-2` for more information.

### 2019-05-13 supplementary_figures/supp_figures.tex
...

  \title{Supplementary Figures}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Pierre-Luc Germain}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{09 Mai, 2019}

@@

\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-4-1.pdf}

@@

\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-5-1.pdf}

@@

The total counts and total features per cell of doublets versus other
cells. We used the demuxlet annotation of doublets (based on SNPs) made
available through CellBench. While doublets tend to have a higher total
count and especially number of detected features, these features alone
are not always sufficient for their identification.

@@

{[}to come{]} \#\#\# Supplementary Figure 3 Doublets that cannot be
identified by our method show lower signs of being doublets.

@@

\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

>>>>

  \title{Supplementary Figures}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Pierre-Luc Germain}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{12 Mai, 2019}

@@

\includegraphics{supp_figures_files/figure-latex/dist_cell_properties-1.pdf}

\vfill

@@

\includegraphics{supp_figures_files/figure-latex/mixology_doublet_featcount-1.pdf}

\vfill

@@

The total counts and total features per cell of doublets (red) versus
other cells. We used the demuxlet annotation of doublets (based on SNPs)
made available through CellBench. The lines indicate, respectively, 2,
2.5, and 3 median absolute deviations. While doublets tend to have a
higher total count and especially number of detected features, these
features alone are not always sufficient for their identification.

@@

\includegraphics{supp_figures_files/figure-latex/featcount_ratio-1.pdf}

\vfill

\hypertarget{supplementary-figure-3-1}{%
\subsubsection{Supplementary Figure 3}\label{supplementary-figure-3-1}}

@@

\includegraphics{supp_figures_files/figure-latex/misclass-1.pdf}
\vspace{1cm}
\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-4-1.pdf}

\vfill

@@

Relationship between various cellular properties and the frequency of
cluster mis-assignment for the mixology10x3cl (A) and mixology10x5cl (B)
datasets. The percentage of misclassification refers to the frequency
with which a given cell is assigned the wrong cluster (using the
Hungarian algorithm for cluster matching) across several hundred
clustering runs with varying parameters. Since some subpopulations tend
to be more misclassified than others, the adjusted rate of
misclassification (\texttt{adj\_mis}) is substracted for the
subpopulation median misclassification rate.

\hypertarget{supplementary-figure-5}{%
\section{Supplementary Figure 5}\label{supplementary-figure-5}}

\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-5-1.pdf}
\vspace{1cm}
\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-6-1.pdf}

\vfill

\hypertarget{supplementary-figure-5-1}{%
\subsubsection{Supplementary Figure 5}\label{supplementary-figure-5-1}}

Relationship between various cellular properties and the frequency of
cluster mis-assignment for the Zheng equal (A) or unequal (B) mixtures
of four cell types. See Supplementary Figure 4 for more information. The
only clear pattern is that cells with a high number of reads or features
tend to have a higher misclassification rate.

\hypertarget{supplementary-figure-6}{%
\section{Supplementary Figure 6}\label{supplementary-figure-6}}

\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-7-1.pdf}

\vfill

\hypertarget{supplementary-figure-6-1}{%
\subsubsection{Supplementary Figure 6}\label{supplementary-figure-6-1}}

Relationship between various cellular properties and the frequency of
cluster mis-assignment for the Zheng mixture of 8 cell types. See
Supplementary Figure 4 for more information.
